Dialect: A Compact Line Notation Based on SMILES

### 2022-05-25 manuscript.tex
Excludes star atoms from DS. closes #101.

Membership of a DS is determined as follows. An atom is added to the DS by setting its \ttt{selected} attribute to \ttt{true} through a process called \textit{selection}. For an atom to be selectable, its \ttt{element} attribute must be contained in the list: \ttt{C}; \ttt{N}; \ttt{O}; \ttt{P}; and \ttt{S}. Atoms having other elements (or \ttt{None}) must not be selected. A bond will be added to the DS if both of its terminals are selected and the \ttt{elided} attribute equals \ttt{true}. No other bond will be added to the DS. This rule allows arbitrary bonds between selected atoms to be excluded from the DS.

>>>>

Membership of a DS is determined as follows. An atom is added to the DS by setting its \ttt{selected} attribute to \ttt{true} through a process called \textit{selection}. For an atom to be selectable, its \ttt{element} attribute must be contained in the list: \ttt{C}; \ttt{N}; \ttt{O}; \ttt{P}; and \ttt{S}. Atoms having other elements must not be selected. A bond will be added to the DS if both of its terminals are selected and the \ttt{elided} attribute equals \ttt{true}. No other bond will be added to the DS. This rule allows arbitrary bonds between selected atoms to be excluded from the DS.

Atoms whose \ttt{element} attribute equals \ttt{None} are not selectable, which prevents their entry into the DS. Bonds to such atoms are similarly excluded. The alternative, conditional inclusion, would complicate both data structures and algorithms for little gain. Exclusion avoids these complexities.
